Respiratory Outbreaks Trends in Toronto Healthcare Institutions Across the COVID-19 Pandemic 

### 2025-05-14 paper/paper.qmd
Finalized results

## Overall Cases:
```{python}
#| label: all-graph
#| tbl-cap: "A line plot on a polar axis"

@@

We see that the total number of cases fluctuates with the number of respiratory cases, with number of outbreaks increasing since 2019 to 2022, and beginning to decrease afterwards.

The number of coronavirus cases also fluctuates with the number of respiratory cases and total cases, following the same trend described above.

## Makeup of Respiratory Outbreaks
```{python}
#| label: composition-chart
#| fig-cap: "Makeup of Respiratory Outbreaks from 2019-2024 inclusive"

@@

It becomes evident that since the end of the pandemic, the proportion of Coronavirus outbreaks compared to non-coronavirus outbreaks has been steadily decreasing.

## Non-Covid Respiratory Outbreaks
```{python}
#| label: no-corona-graph
#| fig-cap: "A line plot on a polar axis"

@@

We see the number of Influenza (A & B), Parainfluenza, Respiratory Syncytial Virus (RSV), Metapneumovirus, and Rhinovirus outbreaks all generally fell to lower levels during the pandemic (2020-2021). 
Post pandemic (2022-2024), all, with the exception of Influenza, have resurged to greater than pre-pandemic (2019) levels. Influenza outbreaks have also increased since the pandemic, but remain at a lower level comparative to 2019.

>>>>

## Overall Cases:
```{python}
#| label: fig-all_plot
#| fig-cap: "Yearly Outbreak Count"

@@

@fig-all_plot showcases that the total number of cases fluctuates with the number of respiratory cases, with number of outbreaks increasing since 2019 to 2022, and beginning to decrease afterwards.
Additionally, the number of coronavirus cases also fluctuates with the number of respiratory cases and total cases, following the same trend described above.

## Makeup of Respiratory Outbreaks
```{python}
#| label: fig-composition_chart
#| fig-cap: "Makeup of Respiratory Outbreaks from 2019-2024 inclusive"

@@

From @fig-composition_chart, it becomes evident that since the end of the pandemic the proportion of Coronavirus outbreaks compared to Non-Coronavirus outbreaks has been steadily decreasing.

## Non-Covid Respiratory Outbreaks
```{python}
#| label: fig-no_corona_graph
#| fig-cap: "Non-Coronavirus Outbreaks"

@@

From @fig-no_corona_graph,  it can be observed that the number of Influenza, Parainfluenza, Respiratory Syncytial Virus, Metapneumovirus, and Rhinovirus outbreaks all generally fell to lower levels during the pandemic (2020-2021). 
Post-pandemic (2022-2024), all, with the exception of Influenza, have resurged to greater than pre-pandemic (2019) levels. Influenza outbreaks have also increased since the pandemic, but remain at a lower level comparative to their 2019 pre-pandemic level.
